Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
fine-tune writing and finalize paper

Similarly, for the plot that maps "Total Reasons for Strip Searching" and "Gender", to ensure that data is proportionate to one another, instead of using `count`, the percentages for each gender group when subdivided into each of the different sums of reasons are calculated. 
Regarding @fig-reasons-gender, intriguingly, the graph calls into question of the above data confirming how males are slightly more likely to be strip searched compared to females when they're arrested. However, when intersected with data like the total number of reasons attributed to strip searches, there appears to be a different narrative. For strip searches that have 0 to 2 reason to be carried out, compared to the 10%, 28% and 29% of males, females prevail at 11%, 32% and 30% respectively. This equates to the fact that females are more frequently strip searched when there are a smaller number of reasons provided for their actions at the time of arrests. Specifically, police more readily strip-search females compared to males even if the severity of their actions may not necessitate strip searching. Yet again, this hints at the potential of strip searching being sexually motivated and gendered, especially when there are mostly male police officers in Toronto [@policeStats] and where strip searching is notoriously regarded as a guise for sexual assault [@stripSearchNSW].

>>>>

Similarly, for the plot that maps "Total Reasons for Strip Searching" and "Gender", to ensure that data is proportionate to one another, instead of using `count`, the percentages for each gender group when subdivided into each of the different sums of reasons are calculated. 
Regarding @fig-reasons-gender, intriguingly, the graph calls into question of the above data confirming how males are slightly more likely to be strip searched compared to females when they're arrested. However, when intersected with data like the total number of reasons attributed to strip searches, there appears to be a different narrative. For strip searches that have 0 to 2 reasons to be carried out, compared to the 10%, 28% and 29% of males, females prevail at 11%, 32% and 30% respectively. This equates to the fact that females are more frequently strip searched when there are a smaller number of reasons provided for their actions at the time of arrests. Specifically, police more readily strip-search females compared to males even if the severity of their actions may not necessitate strip searching. Yet again, this hints at the potential of strip searching being sexually motivated and gendered, especially when there are mostly male police officers in Toronto [@policeStats] and where strip searching is notoriously regarded as a guise for sexual assault [@stripSearchNSW].
